MSSM-Penn-Pitt - ACC and DLPFC - DREAM - FEATURECOUNTS - GRCh38 - CQN - Sparse Model

### 2020-02-19 cmc-rnaseq-de/HBCC_ACC-STG_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
add voom mean-variance plot

VOOM.GENE_EXPRESSION = variancePartition::voomWithDreamWeights(counts = geneExpr, 
                                                               formula = formula,
                                                               data = COVARIATES)

# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)
# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals(ADJUSTED.FIT, CQN.GENE_EXPRESSION$E)

>>>>

VOOM.GENE_EXPRESSION = variancePartition::voomWithDreamWeights(counts = geneExpr, 
                                                               formula = formula,
                                                               data = COVARIATES,
                                                               save.plot = TRUE)
plot(VOOM.GENE_EXPRESSION)
violin_plot <- variancePartition::fitExtractVarPartModel(VOOM.GENE_EXPRESSION,
                                                         formula = formula,
                                                         data = COVARIATES)
plotVarPart(sortCols(violin_plot))

# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

# Residuals after normalisation
RESIDUAL.GENE_EXPRESSION = residuals(ADJUSTED.FIT, CQN.GENE_EXPRESSION$E)

### 2020-02-19 cmc-rnaseq-de/HBCC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
add voom mean-variance plot

VOOM.GENE_EXPRESSION = variancePartition::voomWithDreamWeights(counts = geneExpr, 
                                                               formula = formula,
                                                               data = COVARIATES)

# Fit linear model using new weights and new design
# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

>>>>

VOOM.GENE_EXPRESSION = variancePartition::voomWithDreamWeights(counts = geneExpr, 
                                                               formula = formula,
                                                               data = COVARIATES,
                                                               save.plot = TRUE)
plot(VOOM.GENE_EXPRESSION)
violin_plot <- variancePartition::fitExtractVarPartModel(VOOM.GENE_EXPRESSION,
                                                         formula = formula,
                                                         data = COVARIATES)
plotVarPart(sortCols(violin_plot))

# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

### 2020-02-19 cmc-rnaseq-de/MSSM-Penn-Pitt_ACC_DLPFC_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
add voom mean-variance plot

# Fit linear model using new weights and new design
# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

>>>>

# Fit linear model using new weights and new design
# CQN NA counts to 0 counts for input to dream()
tmp = CQN.GENE_EXPRESSION$E
tmp[is.na(tmp)] = 0
VOOM.GENE_EXPRESSION$E = tmp
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION, 
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE,
                                        save.plot = TRUE)
plot(VOOM.GENE_EXPRESSION)
violin_plot <- variancePartition::fitExtractVarPartModel(VOOM.GENE_EXPRESSION,
                                                         formula = formula,
                                                         data = COVARIATES)
plotVarPart(sortCols(violin_plot))
